ETFA-2007 Author Guidelines for A4 ({\boldmath $21\times29.7$ cm}) Proceedings Manuscripts

### 2014-01-26 Papers_SVN/papers/in_preparation/accepted/2010/cee-timer-giovani/reviewers_questions_and_answers.tex

\documentclass[english,11pt]{letter}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{babel}
\usepackage[top=.5in,bottom=.5in,left=1in,right=1in,noheadfoot]{geometry}
\usepackage{graphicx}
\usepackage{url}

\address{\sffamily
  \begin{tabular}{rr}
    Prof.~Dr.~Ant\^{o}nio Augusto Fr\"{o}hlich & \raisebox{-0.9cm}[0pt][0pt]{\resizebox*{!}{1.2cm}{\includegraphics{lisha}}}\\
    Federal University of Santa Catarina &\\
    Software/Hardware Integration Laboratory &\\
    \multicolumn{2}{r}{PO Box 476, 88040-900 Florian\'{o}polis, SC, Brazil}\\
    \multicolumn{2}{r}{Phone: +55 48 3721-9516}\\
    \multicolumn{2}{r}{E-Mail: guto@lisha.ufsc.br}\\
    \multicolumn{2}{r}{WWW: http://lisha.ufsc.br/Guto}\\
    \\
    \multicolumn{2}{r}{\today}
  \end{tabular}
}

\date{}

\signature{
  \begin{center}
   %\raisebox{-.9cm}[0pt][0pt]{\includegraphics[scale=1]{/home/guto/personal/signature}}\\
    \hrulefill\\
    Ant\^{o}nio Augusto Fr\"{o}hlich
  \end{center}
}

\begin{document}

\begin{letter}{ELSEVIER Computers and Electrical Engineering Journal\\
    Editor-in-Chief\\
    Professor Dr. Manu Malek}
\opening{Dear Prof. Malek,}
\setlength{\parskip}{1.5ex}

Thank you very much for the review of the manuscript \textbf{Periodic
  Timers Revisited: the Real-time Embedded System Perspective}. A
revised version that incorporates all your remarks and also the
reviewers' suggestions is being submitted online. Graphical abstract and
research highlights have been added. The addressing of reviewers'
comments is discussed bellow:

\begin{itemize}
\item \textbf{Precise description of periodic and single-shot
    mechanisms}

  We have extended the explanation about periodic and single-shot timers
  in the introduction and we also included a figure to depict the
  described example.

\item \textbf{Paper's motivation and results}

  We made both motivation and results clearer in the introduction. Our
  main purpose is to weave some of the prejudice against periodic
  timers, which actually owe much of their bad reputation to poor
  implementations. Besides, we present concrete information about the
  limitations of single-shot timers that might be specially useful for
  those endeavoring new real-time support systems.

\item \textbf{Improving related work section}

  We have fully rewritten the related work section, including additional
  timing solutions from other groups and describing each one in more
  detail. Well-known Real-Time Operating Systems (e.g. VxWorks, QNX, RTAI,
  RTLinux) are now featured.

\item \textbf{Motivation for EPOS}

  As we stated in the final remarks of Section 4, a smart implementation
  of a time management mechanism does not depend on the real-time
  operating system. We used EPOS in our experiments because it features
  an elegant and clean implementation that makes additions and
  extensions rather easier than for traditional, non component-based
  systems. An open-source version of EPOS is available online at
  \url{http://epos.lisha.ufsc.br}.

\item \textbf{Conclusions}

  We clearly cited the case where a periodic timer outperforms an
  equivalent single-shot timer (when requested periods exceed the
  maximum hardware period) and also explained why this happens (overhead
  of reprogramming the hardware timer and software tick counting).
  Indeed, we added the result of the multi-threaded environment
  experiment, in which the periodic interrupt handler presented better
  execution timer up to 5 threads in comparison to the single-shot
  interrupt handler.

\item \textbf{Figures placement}

  We made a complete review in the figures placement. We also changed
  the footnote on page 2 by a Figure as recommended by the reviewer \#2.

\item \textbf{Tables 1 and 2}

  We changed the word targeted by expected in Tables 1 and 2 in order to
  improve the comprehension.

\item \textbf{Abbreviations}

  We have added a reference when AVR is used by the first time. AVR is
  not an abbreviation, but the name that Atmel gave for its
  architecture. We also made a review to spell out each acronym in the
  first time it is used.

\end{itemize}

Looking forward to have the manuscript published,

\closing{~}

\end{letter}

\end{document}

### 2014-01-26 Papers_SVN/papers/submitted/tc-unified_design-tiago/tc-2nd_round-rebuttal.tex

\documentclass[english,10pt]{letter}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{babel}
\usepackage[top=.5in,bottom=.5in,left=1in,right=1in,noheadfoot]{geometry}
\usepackage{graphicx,url,color}
\definecolor{Red}{rgb}{.9,0,0}
\definecolor{Green}{rgb}{0,.9,0}
\definecolor{Blue}{rgb}{0,0,.9}
\definecolor{Gray}{rgb}{.8,.8,.8}

\address{\sffamily
\begin{tabular}{p{9.5cm}r}
&Tiago Rogério Mück  and\\
&Prof.~Dr.~Ant\^{o}nio Augusto Fr\"{o}hlich\\
&Federal University of Santa Catarina\\
&Florian\'{o}polis, 88040-000, Brazil\\
&Phone: +55 (48) 3721-9516\\
&E-Mail: \{tiago,guto\}@lisha.ufsc.br\\
    \\
\multicolumn{2}{r}{\today}
\end{tabular}
}

\date{}

\signature{
  %\begin{center}
   %\raisebox{-.9cm}[0pt][0pt]{\includegraphics[scale=1]{}\\
%    \hrulefill\\
%    Tiago~Rogério~Mück~and~Antônio~Augusto~Fröhlich
  %\end{center}
\vspace{-1cm}
\begin{tabular}{p{8cm}}
Tiago Rogério Mück and Antônio Augusto Fröhlich
\end{tabular}
}

\newcommand\rev[1]{Reviewer's comment: {\em #1}}

\begin{document}

\begin{letter}{IEEE Transactions on Computers\\
    Editor-in-Chief\\
    Prof. Dr. Albert Y. Zomaya
}
\opening{Dear Prof. Zomaya,}
\setlength{\parskip}{1.5ex}

A revised version of the manuscript "Unified Design of Hardware and Software Components",
initially submitted to the IEEE Transactions on Computers on July 2012 (log
number TC-2012-06-0397.R1), has just been uploaded through the manuscript submission site under
the title ``Towards Unified Design of Hardware and Software Components Using C++''.

First of all, we would like to thank the reviewers for the detailed discussion. In summary, the
main changes carried out in this resubmission were:

\begin{itemize}
    \item the manuscript title was changed to ``Towards Unified Design of Hardware and Software
Components Using C++''
    \item Figure 2 and the second paragraph in section 4.1 were changed to explain more clearly the
issue of mapping object-oriented design to physical implementations;
    \item To clarify the points highlighted by the reviewers regarding the general applicability of
our approach, major changes were performed in the remaining of section 4 and in section 5:
    \begin{itemize}
        \item We extended the 6th paragraph of section 4.2 and moved it a new section \emph{4.2.1
Scheduler implementation}. This section gives more details about our example;
        \item The explanation of how hardware/software concerns influences component implementations
was improved and moved to section a new section \emph{4.2.2 Scheduler implementation for HW/SW};
        \item Former section 4.2.1 became section 4.2.3;
        \item For improved readability, the scenario adapter example in section 4.3.1 is now part
of a new section \emph{4.3.4 Example: adapting the Scheduler};
        \item The definition of the dispatching aspect was improved to show how different synthesis
tools and interfaces can be supported and abstracted;
       \item We extended section 5 with more details about the implementation of proxies and
agents, emphasizing how different target platforms can be supported;
    \end{itemize}
    \item Case studies description in section 6 is summarized to reduce the section size and make
room for the improvements above;
    \item Improved section 7 with some direction for future work.
\end{itemize}

Please find below a more detailed description of how we have addressed the issues pointed out by
each reviewer.

\textbf{\large Reviewer \#1}

\begin{enumerate}
\item \rev{The examples are not discussed very well. Instead of giving some details, the authors add
some basic literature on programming. For me, this is not a satisfactory response to review and I
cannot understand why the authors did not simply explain their examples.}
\vspace{2mm}

We have reviewed the previous manuscript considering the reviewer opinion. In the revised version,
we have substantially extended the description of our example in section 4.2. The new sections
4.2.1 and 4.2.2 now gives more details about the how hardware/software specific concerns are
detached from the base implementation of the scheduler. Sections 4.3 and 5.1 were also extended in
order to explain how our design artifacts can be used to support different synthesis approaches and
target platforms. We cover this concern in the next answer and in the answer for Review \#3,
comment \#3.

%%%%%%%%%%%%%%%

\item \rev{An important conecern in my review was that the proposed approach is only useful when
using a high-level synthesis tool, which supports synthesis of functions. The authors responded to
this concern by simply adding a sentence that their proposed approach could be used with other
synthesis tools as well. So far, so good, but I am not interested in reading that the proposed
approach could be used with other tools I am interested in understanding how it works.}
\vspace{2mm}

We have extended the description of the dispatching mechanism in section 4.3.1 and given more
details related to its specialization considering different interface synthesis requirements. In the
revised manuscript, Figure 6 illustrates this process and shows specializations for two different
entry-point definitions: one based on a single function and one based on a SystemC module. We believe
this new example gives the reader a clearer understanding on how our static metaprogrammed approach
can be further applied to different C++-based synthesis tools.

\end{enumerate}

\textbf{\large Reviewer \#2}

\begin{enumerate}
\item \rev{The only complain I have is a minor style issue. We now have section 4.2.1, but there is
no section 4.2.2. The authors may want to merge section 4.2.1 into section 4.2.}
\vspace{2mm}

We thank the reviewer for pointing out this issue. This has been addressed in the revised
manuscript.
\end{enumerate}

\textbf{\large Reviewer \#3}

\begin{enumerate}
\item \rev{References to Wikipedia should be replaced by well recognised literature.}
\vspace{2mm}

We have changed the previous references about OOP, UML, and C++ to the following ones:

\begin{verbatim}
 [6] K. Czarnecki and U. W. Eisenecker, Generative programming: methods,
     tools, and applications. New York, USA: ACM Press/Addison-
     Wesley Publishing Co., 2000.
[34] C. Larman, Applying UML And Patterns: An Introduction To Object-
     Oriented Analysis And Design And Iterative Development. Prentice
     Hall PTR, 2005.
[35] A. Alexandrescu, Modern C++ Design: Generic Programming and
     Design Patterns Applied, ser. C++ in-Depth Series.     Addison-
     Wesley, 2001.
\end{verbatim}

%%%%%%%%%%%%%%%

\item \rev{The approach is technically based on C++. For this reason I would propose to modify the
title of the article in the following way: ``Towards a Unified C++-based Design of Hardware and
Software Components''}
\vspace{2mm}

We would like to thank the reviewer for the suggestion. Although the object/aspect oriented domain
decomposition is independent from the implementation language, we agree that our current approach
has been driven by technical characteristics of C++ and the support of HLS tools for C++-based
languages.

%%%%%%%%%%%%%%%

\item \rev{The overall approach is targeted for a specific implemenation platform, as described in
Section 5.2. Still it becomes not clear how the proposed approach supports a separation of the
behaviour/functionality and the mapping to the implementation platform (including certain
artefacts). For instance, a real-time operating system could be considered as platform artefact. For
reuseablilty of the behaviour model (i.e. retargeting to another platform with a different or even
without an operating system) the separation of functionality and structure should be as explicit as
possible. The approach presented in the article seems to be very tailored to the EPOS environment.
If this should be a remaining limitation of the work I would appreciate if you would metion this in
the future work.}
\vspace{2mm}

We presented the platform described in 5.2 as a possible ``implementation instance'' of the
mechanisms mentioned earlier on section 5, however our approach is not limited to that particular
system architecture. Nevertheless, we agree with the reviewer comment since we have skipped some
details on how this portability can be provided. In the revised manuscript, we have improved the
first paragraphs of section 5 and figure 7 in order to illustrate how different implementation
approaches can be encapsulated using templates and static metaprogramming. This encapsulation is
performed by first separating in different classes the component-specific and the platform-specific
behavior of proxies/agents. Different platform-specific behavior is supported by specializing the
related classes in a way in which the correct platform can then be automatically chosen through
configurations provided in system trait classes. A comprehensive example of this approach has also
been added to section 4.3.1 (please, refer to Review \#1, comment \#2)

%%%%%%%%%%%%%%%

\item \rev{In general the conclusion could be significantly improved by a summary of the advantages
and drawbacks of the proposed approach. In an outlook on future work possible solutions for the
mitigation of existing drawbacks could be described. This would definitely further enhance the
quality of the article.}
\vspace{2mm}

Although we have chosen to keep a more conceptual discussion at section 4.4, we extended section
7 to stress the contribution and also provide our prospect for future work:

\begin{verbatim}
  Our future works are twofold. As the comparison
between hardware implementations suggests, new fea-
tures must be considered in order to provide a better
support for high throughput data-oriented applications.
Our main concern with this aspect is on the seamless
integration of stream-oriented interfaces with our object-
oriented modeling approach. Furthermore, though the
application of our design strategy to new cases, we also
aim to identify new hardware/software aspects that can
be encapsulated using the proposed mechanisms.
\end{verbatim}

\end{enumerate}

\vspace{1cm}
\closing{Sincerely,}

\clearpage

\textbf{\large Annex: Changes in the first resubmission}
\vspace{1cm}

Main changes carried out in the first resubmission:

\begin{itemize}
    \item In section 3, we added an explanation about basic OOP concepts and extended the
description of ADESD and AOP;
    \item Minor changes in section 4.1 to make the purpose of Figure 2 clearer;
    \item To clarify the points highlighted by the reviewers and improve the paper organization,
major changes were performed in the remaining of section 4:
    \begin{itemize}
        \item We extended the original section \emph{4.2.1 Component implementation} and merged
its contents in to the top-level section \emph{4.2 Defining C++ unified descriptions};
        \item Concerns related to the limitations of high-level synthesis were moved to a new
section \emph{4.2.1 Synthesis considerations};
        \item We added a paragraph about bit-accurate data types in the new section 4.2.1;
        \item The original subsection 4.2.2 became subsection 4.3 and was extended to provide a
more detailed explanation about our approach to apply hardware/software aspects and to consider
alternative solutions;
        \item Former sections \emph{4.2.3 Wrapping communication} and \emph{4.3 Implementation
flow summary} moved to a new section \emph{5 Deployment of unified components};
        \item We added a new section \emph{4.4 Summary and discussion} that summarizes our approach
and discuss other methods for describing hardware and software in a common language;
    \end{itemize}
    \item We extended section 5 with more details about the implementation of proxies and agents;
    \item Minor changes in section 6 (former section 5):
    \begin{itemize}
        \item Details of the base SoC platform moved to section 5;
        \item Error bars added to measured execution times;
        \item Improved the readability of Table 5;
        \item Minor changes to reduce the section size
    \end{itemize}
\end{itemize}

Please find below a more detailed description of how we have addressed the issues pointed out by
each reviewer.

\textbf{\large Reviewer \#1}

\begin{enumerate}
\item \rev{In my opinion, the main weakness of the paper lies in the presentation of proposed
solution in section 4. Instead of giving general guidelines, the authors only present sample code
snippets, which provide solutions for their running example.}
\vspace{2mm}

We have carefully analyzed the way we present our approach, and we agree that the most general
guidelines were indeed not very clear. In summary, these guidelines consists in the following: 
1) limiting component interaction to method calls allow the creation of a
generic external mechanism; 2) components that require resource allocation must be designed in order
to deal with links to the expected resources, thus allowing such allocation to be performed
externally using the most suitable approach for hardware or software; and 3) the C++ in the unified
implementation must be synthesizable. We have reorganized and extended section 4 in order to make
the considerations above clearer.
\vspace{2mm}

The latter guideline does not affect the actual design of the components, but consists
mostly of coding guidelines that must be followed due to current limitations of high-level
synthesis. Such guidelines were all moved to a new section \emph{4.2.1 Synthesis considerations}.
\vspace{2mm}

The former ones must be considered during the domain decomposition process; otherwise the
incorporation of hardware/software characteristics using the proposed aspect weaving approach would
not be possible. Since explaining the OOP decomposition process itself is not in the scope of this
paper, we have showed the \emph{Scheduler} as a case that satisfies the considerations mentioned
above. In order to make clearer how this is achieved, we have extended the description of the
Scheduler in section \emph{4.2 Defining C++ unified descriptions}. Also, to better demonstrate how
hardware/software characteristics can then be applied in a systematic way using the proposed
scenario adapters, we have reorganized and extended section \emph{4.3 HW/SW aspects
encapsulation}: section 4.3.1 first presents the hardware/software aspects in details; section 4.3.2
then shows their aggregation to build a scenario; and section 4.3.3 describes the scenario adapter
definition. We have also replaced the previous scenario diagram of Figure 4 by a more detailed one
which shows the inheritance/template specialization structure more clearly.
\vspace{2mm}

We have also created a new section \emph{4.4 Summary and discussion}. This section summarizes
our strategy and highlights the points mentioned above. It also includes a discussion suggested in
the comments 2 and 4 from reviewer \#3.

\item \rev{Often, the code snippets are even not discussed at all, which makes it difficult to even
comprehend this particular solution. Especially, I do have problems understanding the Traits example
on page six in the right column.}
\vspace{2mm}

We thank the reviewer for pointing out these issues. We have improved the explanation of all code
snippets. The provided explanations, however, assumes prior knowledge about object-oriented
constructs in C++ and templates. Due to the page limit, we cannot review more general C++ concepts
in the paper. Therefore, we have only added the following footnote (page 3, third paragraph) that
provides some resources to which the reader may refer:

\scriptsize\begin{verbatim}
       1. this paper assumes prior knowledge about OOP, UML and C++.
An overview of the relevant concepts is available at [31], [32], and
[33]. The reader may also refer to [34], [7], and [35] for an indepth
explanation.
\end{verbatim}\normalsize

The following additional references were added:

\begin{verbatim}
[31] "Wikipedia - Class diagram," 2012,
     http://en.wikipedia.org/wiki/Class_diagram.
[32] "Wikipedia - Object-oriented programming," 2012,
     http://en.wikipedia.org/wiki/Object-oriented_programming.
[33] The C++ Resources Network, "Templates," 2012,
     http://www.cplusplus.com/doc/tutorial/templates/.
[34] C. Larman, Applying UML And Patterns: An Introduction To Object-
     Oriented Analysis And Design And Iterative Development. Prentice
     Hall PTR, 2005.
[35] A. Alexandrescu, Modern C++ Design: Generic Programming and
     Design Patterns Applied, ser. C++ in-Depth Series.     Addison-
     Wesley, 2001.
\end{verbatim}

Regarding the specific Traits example, we have extended the explanation of the trait concept in the
second paragraph of section 4.3.2. Additional code examples are provided in sections 4.3.2 and
4.3.3. We have also added a reference to the original proposal of the trait concept, which provides
additional examples:

\begin{verbatim}
[43] N. C. Myers, "Traits: a new and useful template technique," C++
     Report, June 1995. [Online]. Available: http://www.cantrip.org/
     traits.html
\end{verbatim}

\item \rev{No alternative solutions are discussed. This would have been interesting especially for
the static allocation and dispatching aspects. In particular, the proposed dispatching strategy is
very specific for the CatapultC high-level synthesis. Nearly all other HLS tools do not use a single
function signature for describing hardware components. They typically require to present hardware
components as SystemC modules having signal ports or transaction sockets. In this case, the proposed
solution could not be applied directly.}
\vspace{2mm}

We agree with the reviewer in the sense that in our explanation we mentioned only one of the
possible approaches; however, this is not a limitation for our proposal. Our current implementation
of the dispatcher is compliant only with CatapultC since it is the tool used in our experimental
evaluation. Nevertheless, the technical effort to define a top-level SystemC module for another
HLS tool is about the same. To highlight the alternative solutions, we have added the following
sentences in the last paragraph of section 4.3.1: 1) \emph{In Calypto's CatapultC [1] and Xilinx's
AutoESL [5], for instance, the top-level interface of the resulting hardware block (port directions
and sizes) is inferred from a single function signature}; and 2) \emph{Some tools require the
definition of the entry point as a SystemC module with signal ports used to define the IO protocol.
Our current implementation is compliant only with CatapultC, since it is the tool used in our
experimental evaluation. Nevertheless, the Dispatch aspect can be specialized to support different
entry-point requirements and different IO protocols (e.g. two-way handshaking, bus-based, etc). Upon
system generation, the desired dispatcher can be selected using a \emph{Trait}}.
\vspace{2mm}

We have also added more details to Figure 4, which makes clearer the specialization of the
\emph{Dispatch} aspect.

\item \rev{Moreover, why do the authors define their own allocation class while the standard
template library is already providing a ready to use implementation? In summary, by only providing
some examples, it is not clear what exact solution is proposed. Hence, the applicability of the
solution and its limitations remain unclear.}
\vspace{2mm}

In principle, we could have relied on STL; however, current STL implementations are not
synthesizable. Nevertheless we agree that STL should be mentioned in the paper as a possible
alternative. We have added the following sentence in the third paragraph of section 4.3.1: \emph{A
similar approach that uses external allocators for containers such as lists is provided by the C++
standard template library (STL) [42]. In principle, we could have relied on STL; however, current
STL implementations are not synthesizable.}
\vspace{2mm}

Also in section 4.3.1, we have extended the explanation of the List code example and added a code
snippet showing part of the \emph{Static Alloc} aspect implementation.  We believe this will give
the reader a clearer idea of the applicability of our allocators.

\item \rev{Although the paper addresses an important topic and the results clearly show the benefits
of the proposed approach, the presentation of the key contributions is in my opinion too weak to
accept the paper for publication. As only some illustrative examples are given without providing
more general guidelines, the paper looks more like a case study presentation than a research paper.}
\vspace{2mm}

In the answer for comment \#1 we have described how we have addressed these issues. We would like to
thank the reviewer for the constructive comments and we hope that the improvements to the
manuscript will be sufficient to answer the main concerns raised by the reviewer.

\end{enumerate}

\textbf{\large Reviewer \#2}

\begin{enumerate}
\item \rev{Without reading the previous work of the authors it is very hard to get a deeper
understanding of the technical concept and soundness of the approach. Section 3 should better aim on
giving an introduction to the general concepts of aspects and aspect weaving. Currently section 3
points to previous work and gives only little high-level/abstract information.}
\vspace{2mm}

### 2014-01-26 Papers_SVN/papers/in_preparation/accepted/2007/euc2007-hybrid_componentes-hugo/latex8.tex
Versionando o meu mestrado.

% $Id: etfa2006.tex,v 1.1 2005/10/12 14:45:41 cibrario Exp $
%
% Derived from  Author: vasques/sauter, Date: 2000/05/24 15:20:59,
% Revision: 1.4
%
% and updated for better adherence to typesetting guidelines on A4
% paper for ETFA 2006

\documentclass[a4paper,10pt,twocolumn]{article}
\usepackage{etfa2006}
\usepackage{times}

@@

\title{ETFA-2006 Author Guidelines
       for A4 ({\boldmath $21\!\!\times\!\!29.7$ cm}) Proceedings Manuscripts}

\author{First Author\\
Name of Institution 1\\
First line of Institution 1 address\\ Second line of Institution 1 address\\
FirstAuthor@institution1.edu\\
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
\and
Second Author\\
Name of Institution 2\\
First line of Institution 2 address\\ Second line of Institution 2 address\\
SecondAuthor@institution2.edu\\
}

@@

  These last five lines are just to fill out the abstract text to
  exactly 16 lines. These last five lines are just to fill out the
  abstract text to exactly 16 lines. These last five lines are just to
  fill out the abstract text to exactly 16 lines. These last five
  lines are just to fill out the abstract text...
\end{abstract}

@@

Please follow the steps outlined below when submitting your final
manuscript to the ETFA workshop.

@@

The final manuscript of your paper must be submitted through the
electronic submission systems on the conference web page
(http://www.action-m/etfa2006), in pdf format, before June 30th, 
2006.  Please verify if it prints properly on A4 printer paper.

The final manuscript must be accompanied by the registration form, the
signed IEEE copyright release form and also by a proof of the
registration fee payment.  Detailed registration instructions will be
available at the workshop web page.

@@

The length of your paper is limited to 10 two-column pages. For any
extra proceeding pages please contact the ETFA 2006 team
(milena@action-m.com).

@@

All text must be in a two-column format. The total allowable width of
the text area is 17 cm wide by 24.2 cm high.  Columns are to be 8.1 cm
wide, with 0.8 cm space between them.  The main title (on the first
page) should begin 3 cm from the top edge of the page.  The second and
following pages should begin 2.5 cm from the top edge.  On all pages,
the bottom margin should be, at least, 3 cm from the bottom edge of
the page.

@@

MAIN TITLE. The title should be in Times 14-point, boldface type and,
at most, 2 lines long.  Capitalize the first letter of nouns,
pronouns, verbs, adjectives, and adverbs; do not capitalize articles,
co-ordinate conjunctions, or prepositions (unless the title begins with
such a word).  Leave two blank lines after the title.

@@

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing.  All paragraphs should be indented 0.42 cm (1 pica).
Make sure your text is fully justified --- that is, flush left and flush
right.  Please do not place any additional blank lines between
paragraphs. Figure and table captions should be 10-point Helvetica
boldface type as in
%
\begin{figure}[h]
   \caption{Example of caption.}
\end{figure}

\noindent Long captions should be set as in
%
\begin{figure}[h]
   \caption{Example of long caption. It is
     aligned on both sides and indented with an
     additional margin on both sides of 0.42 cm (1~pica).}
\end{figure}

@@

SECOND-ORDER HEADINGS should be Times 10-point boldface, initially
capitalized, flush left, with one blank line before. If you require a
third-order heading (we discourage it), use 10-point Times, boldface,
initially capitalized, flush left, preceded by one blank line,
followed by a period and your text on the same line.

@@

Please use footnotes sparingly and place them at the bottom of the
column on the page on which they are referenced. Use Times 8-point
type, single-spaced.

% Please place a \newpage command in the last page of the paper,
% preferably on a \SubSection or paragraph boundary, in order to
% balance the left and right columns.
\newpage

@@

%-------------------------------------------------------------------------
\nocite{ex1,ex2, ex3, ex4}
\bibliographystyle{etfa2006}
\bibliography{etfa2006}

>>>>

%\documentstyle[times,art10,twocolumn,latex8]{article}

\documentclass[times,10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

@@

\title{ETFA-2007 Author Guidelines 
       for A4 ({\boldmath $21\times29.7$ cm}) Proceedings Manuscripts}

\author{First Author\\
Institution1\\
First line of institution1 address\\ Second line of institution1 address\\ 
FirstAuthor@institution1.edu\\
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
\and
Second Author\\
Institution2\\
First line of institution2 address\\ Second line of institution2 address\\ 
SecondAuthor@institution2.edu\\
}

@@

These last five lines are just to fill out the abstract text to exactly 16 
lines. These last five lines are just to fill out the abstract text to 
exactly 16 lines. These last five lines are just to fill out the abstract 
text...
\end{abstract}

@@

Please follow the steps outlined below when submitting your final 
manuscript to the ETFA conference.

@@

The final manuscript of your paper must be submitted through the electronic 
submission systems on the conference web page, in pdf format. Please 
verify if it prints properly on A4 printer paper.

@@

The length of your paper is limited to 8 two-column pages. For any extra 
proceeding pages please check the conference web page.

@@

All text must be in a two-column format. The total allowable width of the 
text area is 17 cm wide by 24.2 cm high. Columns are to be 8.1 cm wide, 
with 0.8-cm space between them. The main title (on the first page) should 
begin 3 cm from the top edge of the page. The second and following pages 
should begin 2.5 cm from the top edge. On all pages, the bottom margin 
should be, at least, 3 cm from the bottom edge of the page.

@@

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of 
the first page. The title should be in Times 14-point, boldface type. 
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and 
adverbs; do not capitalize articles, coordinate conjunctions, or 
prepositions (unless the title begins with such a word). Leave two blank 
lines after the title.

@@

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use 
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6 
inch or 0.422 cm). Make sure your text is fully justified---that is, 
flush left and flush right. Please do not place any additional blank 
lines between paragraphs. Figure and table captions should be 10-point 
Helvetica boldface type as in
\begin{figure}[h]
   \caption{Example of caption.}
\end{figure}

\noindent Long captions should be set as in 
\begin{figure}[h] 
   \caption{Example of long caption. It is 
     aligned on both sides and indented with an 
     additional margin on both sides of 0.42-cm (1~pica).}
\end{figure}

@@

SECOND-ORDER HEADINGS should be Times 10-point boldface, initially 
capitalized, flush left, with one blank line before, and one after. If you 
require a third-order heading (we discourage it), use 10-point Times, 
boldface, initially capitalized, flush left, preceded by one blank line, 
followed by a period and your text on the same line.

@@

Please use footnotes sparingly%
\footnote
   {%
     Or, better still, try to avoid footnotes altogether.  To help your 
     readers, avoid using footnotes altogether and include necessary 
     peripheral observations in the text (within parentheses, if you 
     prefer, as in this sentence).
   }
and place them at the bottom of the column on the page on which they are 
referenced. Use Times 8-point type, single-spaced.

@@

%------------------------------------------------------------------------- 
\nocite{ex1,ex2}
\bibliographystyle{latex8}
\bibliography{latex8}
